Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-05-25 paper_jasa.tex
power definitions

\red{How are $\Theta_0$ and $\Theta^c_0$ defined? - why do we need them? wouldn't it be better to re-formulate power in terms of acceptance region, not in terms of the parameter space?}
\begin{dfn} \label{dfn:power}
The \textbf{power} of a visual test $V_{\theta}$ is defined as the probability to reject the null hypothesis for a given parameter value $\theta$:
    \begin{equation*}
      \text{Power}_V(\theta)= 
        \begin{cases} 
              \frac1m & \text{if $\theta \in \Theta_0$,} \\
              Pr(\text{Reject } H_0) &\text{if $\theta \in \Theta^c_0$.}
        \end{cases}
    \end{equation*}
\end{dfn}

\noindent For any single observer, the power of a visual test has a lower limit of $\frac1m$ since the probability that an observer will randomly pick the test statistic under $H_0$ is $\frac1m$. When $K$ individuals evaluate a lineup plot independently, the number of successful evaluations, $U \sim \text{Binom} (K,1/m)$  under $H_0$. This leads us to obtain the probability 
\begin{equation}\label{eqn:pvalue}
Pr(U \ge u)= \sum_{k \ge u}^K {{K \choose k} \left(\frac{1}{m}\right)^k\left(1-\frac 1m\right)^{(K-k)}}
\end{equation}
where $u$ is the observed number of successful evaluations. We use this probability to  define the $p$-value for visual test $V_{\theta}$ as follows:
\begin{dfn} \label{dfn:pval}
The $p$-value associated with the decision of a visual test $V_{\theta}$ is given \blue{as the probability to observe a value at least as extreme as the test statistic $u$, 
where $u$ is the number of successful evaluations of the lineup, which leads us to a $p$-value of $P(U \ge u)$ as given in eqn (\ref{eqn:pvalue}). Since $u$ is a discrete value with boundaries 0 and $K$,
 we can also re-formulate the $p$-value in terms of upper and lower boundaries:
 \begin{equation*}
 \begin{array}{rcll}
 P(U \ge u+1) \le &p\text{-value}& (\le 1), & \text{if }u < K, \text{and in particular for } u=0\\
( 0 \le) &p\text{-value}& \le P(U \ge u-1), & \text{if }u > 1, \text{and in particular for } u=K.\\ 
 \end{array}
 \end{equation*}
 }
\red{HH: Tried to re-write it to answer the question below.
Why is the $p$ value not just $Pr(U \ge u)$ ? (We need to modify this a bit with respect to the rejection region $R$, but there should not be a difference in terms of whether we reject or accept. }

    \begin{equation*}
        \begin{cases} 
              p\text{-value} \le Pr(U \ge u)    & \text{when reject $H_0$,} \\
              p\text{-value} > 1-Pr(U \ge u)  & \text{when fail to reject $H_0$}
        \end{cases}
    \end{equation*}
\end{dfn}

%\red{HH: the following paragraph needs some adjustment in terms of t and $\theta$ - could you try to take of that, Mahbub?}\\
\red{For the following paragraph, we wanted to get rid of the absolute value of $t$ and instead look at $t \in R$ and $t \in R^c$.}

>>>>

\red{How are $\Theta_0$ and $\Theta^c_0$ defined? - why do we need them? wouldn't it be better to re-formulate power in terms of acceptance region, not in terms of the parameter space? - $1/m$ also doesn't look right for the power - I think that's just looking at one observer.}
\begin{dfn} \label{dfn:power}
The \textbf{power} of a visual test $V_{\theta}$ is defined as the probability to reject the null hypothesis for a given parameter value $\theta$:
    \begin{equation*}
      \text{Power}_V(\theta)= 
        \begin{cases} 
              \frac1m & \text{if $\theta \in \Theta_0$,} \\
              Pr(\text{Reject } H_0) &\text{if $\theta \in \Theta^c_0$.}
        \end{cases}
    \end{equation*}
\end{dfn}

\red{Alternative Power definition:}
\begin{dfn} \label{dfn:power}
The \textbf{power} of a visual test $V_{\theta}$ is defined as the probability to reject the null hypothesis for a given parameter value $\theta$:
    \begin{equation*}
      \text{Power}_V(\theta)= Pr(\text{Reject } H_0) = P(X \ge x_{1-\alpha}) = 
        \begin{cases} 
               1 - \text{Binom}_{K, 1/m}(x_{1-\alpha} - 1) & \text{ if } H_0 \text{ is true }.\\
              1 - F_{X, \theta} (x_{1-\alpha} - 1) & \text{ if } H_1 \text{ is true}.
        \end{cases}
    \end{equation*}
\end{dfn}

\red{Note that $F_{X, \theta}$ is the distribution of $X$ under the alternative with given parameter value $\theta$.}

%\noindent For any single observer, the power of a visual test has a lower limit of $\frac1m$ since the probability that an observer will randomly pick the test statistic under $H_0$ is $\frac1m$. When $K$ individuals evaluate a lineup plot independently, the number of successful evaluations, $U \sim \text{Binom} (K,1/m)$  under $H_0$. This leads us to obtain the probability 
%\begin{equation}\label{eqn:pvalue}
%Pr(U \ge u)= \sum_{k \ge u}^K {{K \choose k} \left(\frac{1}{m}\right)^k\left(1-\frac 1m\right)^{(K-k)}}
%\end{equation}
%where $u$ is the observed number of successful evaluations. We use this probability to  define the $p$-value for visual test $V_{\theta}$ as follows:
%\begin{dfn} \label{dfn:pval}
%The $p$-value associated with the decision of a visual test $V_{\theta}$ is given \blue{as the probability to observe a value at least as extreme as the test statistic $u$, 
%where $u$ is the number of successful evaluations of the lineup, which leads us to a $p$-value of $P(U \ge u)$ as given in eqn (\ref{eqn:pvalue}). Since $u$ is a discrete value with boundaries 0 and $K$,
% we can also re-formulate the $p$-value in terms of upper and lower boundaries:
% \begin{equation*}
% \begin{array}{rcll}
% P(U \ge u+1) \le &p\text{-value}& (\le 1), & \text{if }u < K, \text{and in particular for } u=0\\
%( 0 \le) &p\text{-value}& \le P(U \ge u-1), & \text{if }u > 1, \text{and in particular for } u=K.\\ 
% \end{array}
% \end{equation*}
% }

%\red{HH: Tried to re-write it to answer the question below.
%Why is the $p$ value not just $Pr(U \ge u)$ ? (We need to modify this a bit with respect to the rejection region $R$, but there should not be a difference in terms of whether we reject or accept. }
%
%    \begin{equation*}
%        \begin{cases} 
%              p\text{-value} \le Pr(U \ge u)    & \text{when reject $H_0$,} \\
%              p\text{-value} > 1-Pr(U \ge u)  & \text{when fail to reject $H_0$}
%        \end{cases}
%    \end{equation*}
%\end{dfn}

%\red{HH: the following paragraph needs some adjustment in terms of t and $\theta$ - could you try to take of that, Mahbub?}\\
%\red{For the following paragraph, we wanted to get rid of the absolute value of $t$ and instead look at $t \in R$ and $t \in R^c$.}

\red{The following considerations deal with assessing the `difficulty' of  a lineup of size $m$. I think it's very relevant, but I don't see a natural equivalent in the classical testing situation.}
